---
title: "Markdown: Titanic Case Study"
author: "Louise Lai"
date: "July 13, 2018"
output: pdf_document
---
This is my first R Markdown document for **MSDS 593**. I am required to submit all **MSDS 593** homework in RMarkdown.

Firstly, I am going to generate an `html` document as output, set in the YAML header section of this document. Secondly, I am **NOT** hardcoding the date, but rather using a function which will automatically print the current date on the day the document is knit.

Now, I am going to import a dataset about passengers from the Titanic, using the following line of code:
```{r setup, include=FALSE}
read.csv("~/Desktop/programming/USF/exploratory/Exploratory-Data-Analysis-with-R/courseData/titanic.csv")
```

This fails for a few reasons, nameline, I read the file and stored it nowhere. So I wasted my time waitinf for R ro read in the file, and then when it finally did, it printed the rows of data to the Console window, and viola, the data disappeared faster than it loaded. Now I know better.

```{r setupBetter, include=FALSE}
titanicData <- read.csv("~/Desktop/programming/USF/exploratory/Exploratory-Data-Analysis-with-R/courseData/titanic.csv")
```

`titanicData` has `r nrow(titanicData)` and `r ncol(titanicData)` columns. All variables in the data frame are listed here using `str()`.
```{r echo=FALSE}
str(titanicData)
```

```{r, include=FALSE}
nMale <- sum(titanicData$Sex == 'male')
nFemale <- sum(titanicData$Sex == 'female')
percentMale <- nMale / (nMale+nFemale)
percentFemale <- 1 - percentMale
```

The Titanic had `r nmale` male passengers 







## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
